Gafo-cc visuals

### 2022-12-05 analysis/gafo-cc-data-processing.Rmd
update repo

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

```{r demographics}
raw_demographics_namibia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/namibia/GaFo Data Haikom 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe")
  )

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  mutate(
    ageInYears = as.numeric(difftime(TestDate,BirthDate, units = "days")/365.25),
  ) %>%
  rename(subjID = ID) %>% 
  select(-c(`First Name`, Name, BirthDate, TestDate, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))

@@

```{r}
data_namibia <- tidy_demographics_namibia%>%
  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))
```

@@

```{r}
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-leipzig/data/ ~/Work/Local/Quantex/Gafo/raw_data/gafo-cc/leipzig/")
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) #%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

@@

data <- bind_rows(
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_zambia
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

@@

```{r}
mdata <- data%>%
  filter(community == "leipzig" | community == "akure",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status))

@@

mdata%>%
  filter(is.na(agecentered))

mdata%>%
  filter(trialnr == 5)%>%
  select(subjid,agecentered)
```

>>>>

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = toupper(subjID))%>%select(-touchScreen)#%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

```{r demographics}
raw_demographics_namibia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Haikom 2022.xlsx", sheet = 1, col_types = c("numeric", "text", "text", "text", "date", "date", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1, col_types = c("numeric", "text", "text", "text", "date", "date", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe"),
    read_xlsx("../../raw_data/gafo-cc/namibia/Data Windhoek 2022 completed.xlsx", sheet = 1)%>%
    select(ID, Community,`First Name`,Name,	BirthDate,	TestDate,	Sex,	Screen,	Touchscreen,	Household,	Children,	YoungerChildren)%>%mutate(ID = paste0("W",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "windhoek")
  )%>%
  filter(!grepl("rop",Comment))

testdates <- tidy_data_namibia%>%
  select(subjID, timestamp)%>%
  mutate(test_date = as.Date(substr(timestamp, 0,10)))%>%
  select(subjID, test_date)%>%
  distinct(subjID, .keep_all = T)%>%
  mutate(subjID = toupper(subjID))

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  rename(subjID = ID)%>%
  left_join(testdates)%>%
  mutate(
    ageInYears = as.numeric(difftime(test_date,BirthDate, units = "days")/365.25),
  ) %>%
  select(-c(`First Name`, Name, BirthDate, TestDate,test_date, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_namibia <- tidy_demographics_namibia%>%
  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = T)

@@

@@

```{r}
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-leipzig/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/leipzig/")
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))%>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
  ) %>%select(-touchScreen)#%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

# Stanford

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(screen == "touchscreen", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)
```

@@

data <- bind_rows(
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_zambia,
  data_stanford
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

```{r}
data%>%
  select(-touchscreen)%>%
  filter(community == "windhoek")%>%
  rename(touchscreen = touchscreen.x)%>%
  group_by(subjid, community, sex, screen, touchscreen, household,children,younger_children, ageinyears)%>%
    summarise(precision = mean(abs(clickdistfromtargetcenterx)))%>%
  write_csv(.,"../data/gafo-cc-windhoek.csv")
```

@@

```{r}

data <- read_csv("../data/gafo-cc-clean-data.csv")

mdata <- data%>%
  filter(community == "leipzig" | community == "akure",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site))

@@

display(communities)%>%
  filter(is.na(community))

mdata%>%
  filter(trialnr == 5)%>%
  select(subjid,agecentered)

range(mdata$clickscaledx+500)
```

### 2022-12-05 analysis/gafo-cc-visuals.Rmd
update repo

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")
```

@@

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "")+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "bottom")

```
```{r}
ggsave("../visuals/dev_site.png", width = 5, height = 6, bg = "white")
```

@@

```{r}
ptp <- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Binned target position", y = "Mean imprecision")+
  scale_color_colorblind()+
  #ylim(0,1000)+
  theme_minimal()
```

```{r}
pscreen1 <- data%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(community, subjid, predictor, value)%>%
  summarise(mean= mean(abs(clickdistfromtargetcenterx)))

pscreen2 <- data%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(community, predictor, value)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(pscreen%>%filter(!is.na(value)), aes(x = value, y = mean, col = community))+
  geom_point(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean, col = community), pch = 1, alpha = .5, position = position_dodge(width = .5))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5))+
  facet_grid(~predictor, scales = "free_x")+
  scale_x_discrete(labels = c("no", "yes"))+
  scale_color_colorblind()+
  #ylim(0,1000)+
  theme_few()
```

```{r}
pred <- data%>%
  group_by(community, subjid, household, children, younger_children)%>%
  summarise(mean= mean(abs(clickdistfromtargetcenterx)))%>%
  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
  group_by(community,predictor)%>%
  mutate(value = scale(value))

ggplot(pred, aes(x = value, y = mean, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  facet_grid(~predictor, scales = "free_x")+
  stat_cor()+
  scale_color_colorblind()+
  ylim(0,1000)+
  theme_minimal()
```

>>>>

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)"))
```

@@

```{r}
data%>%
  filter(community != "chimfunshi (sambia)")%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(alpha = .25)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "Community")+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "right")

```
```{r}
ggsave("../visuals/dev_site.png", width = 8, height = 6, bg = "white")
```

@@

```{r}
ggsave("../visuals/dev_site.png", width = 8, height = 6, bg = "white")
```

```{r}
ptp<- data%>%
  filter(community != "chimfunshi (sambia)")%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
  scale_color_colorblind(name = "Community")+
  ylim(0,1000)+
  theme_minimal()
```

```{r}
ggsave("../visuals/target_position_site.png", width = 8, height = 6, bg = "white")
```

```{r}
pscreen1 <- data%>%
  group_by(community)%>%
  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)))%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(subjid, predictor, value)%>%
  summarise(mean= mean(clickdistfromtargetcenterx))

pscreen2 <- data%>%
  group_by(community)%>%
  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)))%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(predictor, value)%>%
  tidyboot_mean(col= clickdistfromtargetcenterx)

ggplot(pscreen2%>%filter(!is.na(value)), aes(x = value, y = mean))+
  geom_jitter(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean), pch = 1, alpha = .25, height = 0)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5), col = "firebrick")+
  facet_grid(~predictor, scales = "free_x")+
  scale_x_discrete(labels = c("no", "yes"))+
  labs(y = "Imprecision (scaled within community)", x = "Predictor value")+
  scale_color_colorblind()+

  #ylim(0,1000)+
  theme_bw()
```

```{r}
ggsave("../visuals/pred_screen.png", width = 8, height = 6, bg = "white")
```

```{r}
pred <- data%>%
  group_by(community)%>%
  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)), 
         household = scale(household), 
         children = scale(children),
         younger_children = scale(younger_children))%>%
  group_by(subjid, household, children, younger_children)%>%
  summarise(mean= mean(clickdistfromtargetcenterx))%>%
  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
  group_by(predictor)%>%
  mutate(value = scale(value))

ggplot(pred, aes(x = value, y = mean))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  facet_grid(~predictor, scales = "free_x")+
  stat_cor()+
  scale_color_colorblind()+
  labs(y = "Imprecision (scaled within community)", x = "Predictor value (scaled within community)")+
  #ylim(0,1000)+
  theme_bw()
```

```{r}
ggsave("../visuals/pred_household.png", width = 12, height = 6, bg = "white")
```
